Comparison of the solution of the shallow equation with experimental

### 2015-03-09 doc/paper/paper.tex
Fixed figure file naming and location
add a plots in paper.tex

Figure \ref{fig:waveheight_nocolumn} shows the time history of the wave height measured at the center location where the column will be mounted. 
Result from geoclaw agree quite well in general. At around t=3.8, geoclaw accurately predicted the arrival of the shock. 
As for the peak value of this shock, geoclaw overestimated it a little, while OpenFOAM, another open source computational fluid dynamics software gave a better value by solving the Navier-Stokes equations with turbulent model.
After a longer time, the wave gets reflected at the right wall of the tank, which can be seen by the second jump in wave height in the figure. 
Geoclaw also predicted the arrival time of this peak quite well and got only a little overestimation of the peak value.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../../dambreak/myplot/waveheight_nocolumn}
    \caption{time history of wave height for case without a column}
    \label{fig:waveheight_nocolumn}
\end{figure}

Figure \ref{fig:velocityU_nocolumn} gives the time history of the streamwise velocity $u$ from geoclaw and experiment. 
Note that this velocity $u$ in both geoclaw and experiment are depth-averaged. 
Geoclaw accurately predicted the time of the velocity peak as well as the value of the peak. 
After the peak arrived, geoclaw overestimated the value of velocity.
The reason why geoclaw gives a higher velocity may be attributed to its depth-averaged property: water at all depth are propagating with the same speed. In the experiment, the velocity gets smaller as it comes closer to the bottom. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../../dambreak/myplot/velocityU_nocolumn}
    \caption{time history of streamwise velocity U for case without a column}
    \label{fig:velocityU_nocolumn}
\end{figure}

\section{Dam Break with square column}\label{Sec:Square}
Figure \ref{fig:waveheight_square_x=11.0} gives a comparison of the time history of the wave height measured at 0.04m ahead of the leading edge of the square column.(0.1m ahead of center of the column)
Note that this figure is from t=3.0 to t=4.0, which is quite a short range compared to the previous figures.
There are two jump in result given by geoclaw. First jump change water level from around 0.02 to 0.1, second one jump from 0.1 to a higher level of around 0.22.
If we recall that the wave height is around 0.1 in \ref{fig:waveheight_nocolumn}, we can confirm this first jump is cause by the arrival of shock wave caused by dambreak. The second jump is induced by wave reflected by the column.  
%todo
If we compare the time interval between first jump and second jump with that in \ref{}, we can see that as the gauge gets closer to column, this time interval also gets shorter.
%
The arrival time of the peak predicted by geoclaw is about 0.2 second earlier than the time measured from experiment and in experiment, the jump is more like a a smooth increase. 
This can be explained by the difference between the shallow water equations that geoclaw solves and N-S equations that better describe the physics.
In shallow water equations, fluid viscosity is not taken into account, while it's significant in N-S equation (or real physics).
This causes the shock remain its shape in as it propagates in shallow water equation and smooth out in experiment.
Thus we see a jump in result from shallow water equation while a smooth increase in experiment result.
Shallow water equation is essentially a hyperbolic PDE, whose solution depends on initial condition along characteristics in spatio-temporal domain. 
Thus before the propagating shock arrive, all water downstream the shock stays still. In other words, it even does not know there is a column before the shock hits the column. In contrast, N-S equation is a elliptic PDE. 
In real physics govened by N-S equation, when front of the shock wave gets close to the column, water downstream it and upstream column are affected and resist the comming of wave to some extent, which raises the wave hegiht even before the wave hits the column.   
This explains why we cannot see two jumps in experiment results.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_square_x=11}
    \caption{time history of wave height for case with square column}
    \label{fig:waveheight_square_x=11.0}
\end{figure}

\section{Dam Break with cylinder column}\label{Sec:Cylinder}
Figure \ref{fig:waveheight_cylinder_x=11.0} is the time history of the wave height measured at 0.04m ahead of the leading edge of cylinder column.(0.1m ahead of the center of the column)
Since the way geoclaw treat a cell partly belong to cylinder and partly belong to tank bottom is to give that cell an average value of topography from cylinder and tank bottom based on area ratio, we get a quasi-circle actually instead of circle. Thus the result in this case does not agree well with the experiment result. 
Future test can be conducted by setting a higher level for mesh refinement to get a better circle.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_cylinder_x=11}
    \caption{time history of wave height for case with cylinder column}
    \label{fig:waveheight_cylinder_x=11.0}
\end{figure}

>>>>

Figure \ref{fig:waveheight_nocolumn} shows the time history of the wave height measured at the center location where the column will be mounted. 
Result from geoclaw agree quite well in general. At around t=3.8, geoclaw accurately predicted the arrival of the shock. 
As for the peak value of this shock, geoclaw overestimated it a little, while OpenFOAM, another open source computational fluid dynamics software gave a better value by solving the Navier-Stokes equations with turbulent model.
After a longer time, the wave gets reflected at the right wall of the tank, which can be seen by the second jump in wave height in the figure. 
Geoclaw also predicted the arrival time of this peak quite well and got only a little overestimation of the peak value.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_nocolumn}
    \caption{time history of wave height for case without a column}
    \label{fig:waveheight_nocolumn}
\end{figure}

Figure \ref{fig:velocityU_nocolumn} gives the time history of the streamwise velocity $u$ from geoclaw and experiment. 
Note that this velocity $u$ in both geoclaw and experiment are depth-averaged. 
Geoclaw accurately predicted the time of the velocity peak as well as the value of the peak. 
After the peak arrived, geoclaw overestimated the value of velocity.
The reason why geoclaw gives a higher velocity may be attributed to its depth-averaged property: water at all depth are propagating with the same speed. In the experiment, the velocity gets smaller as it comes closer to the bottom. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/velocityU_nocolumn}
    \caption{time history of streamwise velocity U for case without a column}
    \label{fig:velocityU_nocolumn}
\end{figure}

\section{Dam Break with square column}\label{Sec:Square}
Figure \ref{fig:waveheight_square_x=11.0} gives a comparison of the time history of the wave height measured at 0.04m ahead of the leading edge of the square column.(0.1m ahead of center of the column)
Note that this figure is from t=3.0 to t=4.0, which is quite a short range compared to the previous figures.
There are two jumps in result given by geoclaw. First jump change water level from around 0.02 to 0.1, second one jump from 0.1 to a higher level of around 0.22.
If we recall that the wave height is around 0.1 in \ref{fig:waveheight_nocolumn}, we can confirm this first jump is cause by the arrival of shock wave caused by dambreak. The second jump is induced by wave reflected by the column.  
If we compare the time interval between first jump and second jump with that in \ref{fig:waveheight_square_x=11.02}, we can see that as the gauge gets closer to column, this time interval also gets shorter.
The arrival time of the peak predicted by geoclaw is about 0.2 second earlier than the time measured from experiment and in experiment, the jump is more like a a smooth increase. 
This can be explained by the difference between the shallow water equations that geoclaw solves and N-S equations that better describe the physics.
In shallow water equations, fluid viscosity is not taken into account, while it's significant in N-S equation (or real physics).
This causes the shock remain its shape in as it propagates in shallow water equation and smooth out in experiment.
Thus we see a jump in result from shallow water equation while a smooth increase in experiment result.
Shallow water equation is essentially a hyperbolic PDE, whose solution depends on initial condition along characteristics in spatio-temporal domain. 
Thus before the propagating shock arrive, all water downstream the shock stays still. In other words, it even does not know there is a column before the shock hits the column. In contrast, N-S equation is a elliptic PDE. 
In real physics govened by N-S equation, when front of the shock wave gets close to the column, water downstream it and upstream column are affected and resist the comming of wave to some extent, which raises the wave hegiht even before the wave hits the column.   
This explains why we cannot see two jumps in experiment results.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_square_x11}
    \caption{time history of wave height for case with square column}
    \label{fig:waveheight_square_x=11.0}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_square_x1102}
    \caption{time history of wave height for case with square column, at x = 11.02}
    \label{fig:waveheight_square_x=11.02}
\end{figure}

\section{Dam Break with cylinder column}\label{Sec:Cylinder}
Figure \ref{fig:waveheight_cylinder_x=11.0} is the time history of the wave height measured at 0.04m ahead of the leading edge of cylinder column.(0.1m ahead of the center of the column)
Since the way geoclaw treat a cell partly belong to cylinder and partly belong to tank bottom is to give that cell an average value of topography from cylinder and tank bottom based on area ratio, we get a quasi-circle actually instead of circle. Thus the result in this case does not agree well with the experiment result. 
Future test can be conducted by setting a higher level for mesh refinement to get a better circle.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_cylinder_x11}
    \caption{time history of wave height for case with cylinder column}
    \label{fig:waveheight_cylinder_x=11.0}
\end{figure}
